Review: Adaptive Introgression Expanded the Genetic Base of Crops during post-Domestication Spread

### 2017-07-05 paper.tex
edits to future studies

Research has so far shown that adaptive crop-wild introgression has played a significant role in the domestication histories of many agronomically-important crops.
However, the dynamics of the process in these cases are not yet fully understood.
To what extent does the level of introgression across taxa depend on divergence time and/or mutation load between donor and recipient taxa?
Can colonizing species and/or hybrid swarms serve as bridges for gene flow between previously allopatric taxa?
At what geographic scale does adaptive introgression occur?
Is introgression frequently restricted to very local populations, or is it often seen over broad geographic ranges?
To what extent does this depend on the slope of environmental gradients such as temperature, precipitation, and elevation?
How did the conscious, subconscious, and unconscious decisions of early farmers facilitate or hinder adaptive introgression into their crops during early domestication?
How do the practices of contemporary farmers affect the process of adaptive introgression today?

Additional study of introgression in agroecosystems could lead to advances in both basic and applied genetics, and specifically the continued improvement of modern crops.
Loci underlying the domesticated phenotype can be more clearly identified by removing the confounding population genetic signal of introgression.
These loci are potentially beneficial targets for crop improvement.
Furthermore, adaptive introgression that is clearly tied to a specific environment may include beneficial alleles that can be utilized in crop breeding.

>>>>

Basic:
We're beginning to see the introgression has occurred across a number of crops during their expansion.
What is the genomic architecture of this introgression and does the architecture suggest it's been adaptive?
At what geographic scale is introgression adaptive?  Is it very local?  Do you see different architectures of introgression across different regions?
At what taxonomic scale does introgression occur?  When do species become so diverged that introgression is either not possible or maladaptive?

Research has so far shown that adaptive crop-wild introgression has played a significant role in the domestication histories of many agronomically-important crops.
However, the dynamics of the process in these cases are not yet fully understood.
To what extent does the level of introgression across taxa depend on divergence time and/or mutation load between donor and recipient taxa?
At what geographic scale does adaptive introgression occur?
Is introgression frequently restricted to very local populations, or is it often seen over broad geographic ranges?
To what extent does this depend on the slope of environmental gradients such as temperature, precipitation, and elevation?

Applied:
Additional study of introgression in agroecosystems could lead to advances in both basic and applied genetics, and specifically the continued improvement of modern crops.
Loci underlying the domesticated phenotype can be more clearly identified by removing the confounding population genetic signal of introgression.
These loci are potentially beneficial targets for crop improvement.
Furthermore, adaptive introgression that is clearly tied to a specific environment may include beneficial alleles that can be utilized in crop breeding.
